Missing data: Current practice in football research and recommendations for improvement

### 2020-09-03 paper/paper.Rmd
adjust title and conflict of interest: closes #9

---
title: "Missing data: Current practice in football research and recommendations for reporting missingness"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

NJT naniar package?

>>>>

---
title: "Missing data: Current practice in football research and recommendations for improvement"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@
